 

### 2021-07-10 vertical-thermal-review.Rmd
Update vertical-thermal-review.Rmd

Leaf metabolism is strongly shaped by leaf temperature, and by the traits and environmental drivers reviewed above, all of which vary across vertical forest gradients (Fig. `r fig_schematic`). 
However, as we detail below, very few studies have valued temperature responses of leaf metabolic rates along a vertical canopy gradient, or compared sun and shade leaves (Table `r table_leaf_metabolism`).

>>>>

Leaf metabolism is strongly shaped by $T_{leaf}$, and by the traits and environmental drivers reviewed above, all of which vary across vertical forest gradients (Fig. `r fig_schematic`). 
However, as we detail below, very few studies have valued temperature responses of leaf metabolic rates along a vertical canopy gradient, or compared sun and shade leaves (Table `r table_leaf_metabolism`).
